---
title: "My first website"
author: "xinyi zheng"
date: "2023-10-30"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---
# Introduction
Hello, I am Xinyi. This is my first website. 
My UNI is xz3298. 

My email: xz3298@cumc.columbia.edu

My github account is [XinyiZheng7](https://github.com/XinyiZheng7)

I major in [Environmental Health Data Science](https://www.publichealth.columbia.edu/academics/degrees/master-science/environmental-health-data-science)

Also, I give a brief introduction of my academic and professional experience in the below 

# My academic and professional experience

* [About me](about.html)


I don’t know what to say first, but I need to leave some text and pictures here, so I leave a poem:


My steadfast lover, true, with no regret's sound,

Hear my whisper soft as your eyes lead the way—

Ahead, dark thorns and mires do abound,

Yet dreams of splendor past, behind you lay.

# Here are three plots
## First, load necessary packages:
```{r}
library(p8105.datasets)
library(flexdashboard)
library(plotly)
library(dplyr)
library(tidyverse)
```
## Importing and cleaning the dataset:
```{r}
data(ny_noaa)

ny_noaa_subset <- ny_noaa %>%
  filter(!is.na(prcp), !is.na(snow), !is.na(tmax), !is.na(tmin),date>="2010-01-01")

```

## Scatter Plot (Date and Snowfall)
```{r}
plot_ly(ny_noaa_subset, x = ~date, y = ~prcp, type = "scatter", mode = "markers") %>%
  layout(title = "Date vs. Snowfall in 2010",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Prcp"))
```

## Barchart (Date and Precipitation)
```{r}
agg_data <- aggregate(ny_noaa$prcp ~ format(ny_noaa$date, "%Y"), FUN=sum)

plot_ly(agg_data, labels = ~format(as.Date(ny_noaa$date, format="%Y-%m-%d"), "%Y"), values = ~ny_noaa$prcp, type = 'pie') %>%
  layout(title = 'Total Precipitation per Year')
```

## Bar Chart (tmax and tmin)
```{r}
plot_ly(data = ny_noaa_subset, x = ~id, y = ~snow, type = 'bar', colors = 'viridis') %>%
  layout(title = "Snow amount in 2010 per location", xaxis = list(title = "location"), yaxis = list(title = "Snow amount"))
```